---
title: "Assignment7"
author: "Joyce Aldrich"
date: "2022-11-06"
output: html_document
---
Assigment: 
In this assignment, you should start by getting the primary example code from chapter 2 working in an R Markdown document.  You should provide a citation to this base code.  
You’re then asked to extend the code in two ways:
1. Work with a different corpus of your choosing, and
2. Incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).


```{r}
library(tidytext)
library(textdata)
```

```{r}
get_sentiments("afinn")
```
```{r}
get_sentiments("bing")
```

```{r}
get_sentiments("nrc")
```

#loading the novels from author Jane Austen
```{r}
library(janeaustenr)
library(dplyr)
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```

#corresponding list of positive sentiment words in Austen’s novel Emma.
```{r}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

# using the bing lexicon, the novels are plotted according to the sentiments of each line.
```{r}
library(tidyr)

jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```
```{r}
library(ggplot2)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```
Conclusion: Per the plot above, we found that Jane Austen novels are toward postive than negative. 

# tidy the book Pride and Prejudice
```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")
```

#use sentiment lexicons and examine how the sentiment changes across the Pride and Prejudice
```{r}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```
# comparison of each lexicon.
```{r}
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```
Conclusion: Per the plot above, we found that NRC is more positive sentiment for this book. 


# Look briefly for positive and negative words in these two lexicons
```{r}
get_sentiments("nrc") %>% 
  filter(sentiment %in% c("positive", "negative")) %>% 
  count(sentiment)
```

```{r}
get_sentiments("bing") %>% 
  count(sentiment)
```
```{r}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
```

# comparison of negative and positive count
```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

```{r}
custom_stop_words <- bind_rows(tibble(word = c("miss"),  
                                      lexicon = c("custom")), 
                               stop_words)

custom_stop_words

```
# wordcloud 
```{r}
library(wordcloud)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```
```{r}
library(reshape2)

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```
# extension analysis for book Persuasion 
# there is an issue for me to install "gutenbergr" package
```{r}

persuasion <- tidy_books %>% 
  filter(book == "Persuasion")

```

#use sentiment lexicons and examine how the sentiment changes across the book
```{r}
afinn_2 <- persuasion %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc_2 <- bind_rows(
 persuasion %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  persuasion %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```
#comparsion of each lexicon.
```{r}
bind_rows(afinn_2, 
          bing_and_nrc_2) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```
Conclusion: Overall, we found that NRC again is more positive sentiment for this book as well. 

```{r}
bing_word_counts_2 <- persuasion %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts_2
```


#wordcloud for all words in Persuasion 
```{r}
library(wordcloud)

tidy_books %>%
 filter(book == "Persuasion") %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```
Conclusion: We found that NRC  is more positive sentiment lexicon than "bing" and "afinn" forpersuasion and pride_prejudice books.

